Q1: Are lake and terrestrial primary productivity coherent?

### 2020-01-07 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam.Rmd
update figure for manuscript

source("~/GitHub/AquaTerrSynch/AnalysisCode/bandtest_coh.R")

@@

@@

#plotting
tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions_20191031.tif", units="in",
     res=300, width=6.5, height=6.5)

par(mar=c(3,3,2,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),cex.main=0.9)

@@

par(mar=c(1,1,2,1))
rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phases",
       at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
text(0.9*par()$usr[1],0.95*par()$usr[4],"c)")
rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phases",
     at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
text(0.9*par()$usr[1],0.95*par()$usr[4],"d)")

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map.tif",units="in",
     res=300, width=3.25, height=2.75)
par(mar=rep(0,4))
plot(lagosstates, main="",bty="o")
points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.45, col="black",bg="grey")
legend("bottomright",pch=c(0,21),col="black",pt.bg="grey",legend=c("States in LAGOS-NE","Selected lakes"),inset=c(0.025,0.01),bty="n")
dev.off()

@@

#huc2 and huc4 watershed codes
huc_codes<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')

@@

bight=5.5
bigwd=9

@@

png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png", units="in",
     res=300, width=bigwd/5, height=bight/4)
par(mar=c(0,0,1,0))
plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),
     ylim=c(1454000,3012981),lwd=0.5)
lines(lagosstates_prj,lwd=0.5)
par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex.axis=0.7)
dev.off()

png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png", units="in",
     res=300, width=bigwd/5, height=bight/4)
par(mar=c(0,0,1,0))
plot(huc_bdys_cohlt,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohlt$coeff)],xlim=c(-91837,2260000),
     ylim=c(1454000,3012981),lwd=0.5)
lines(lagosstates_prj,lwd=0.5)
par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohlt$coeff), max(huc_bdys_cohlt$coeff), length.out=5),2), cex.axis=0.7)
dev.off()

png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png", units="in",
     res=300, width=bigwd/5, height=bight/4)
par(mar=c(0,0,1,0))
plot(huc_bdys_sinphilt,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys_sinphilt$coeff)],xlim=c(-91837,2260000),
     ylim=c(1454000,3012981),lwd=0.5)
lines(lagosstates_prj,lwd=0.5)
par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_sinphilt$coeff), max(huc_bdys_sinphilt$coeff), length.out=5),2), cex.axis=0.7)
dev.off()

panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png")
panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png")
panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png")

mar1<-c(3,1.5,0.5,0.2)
fudge=1/34

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_landscape.tif",units="in",res=300,width=bigwd, height=bight)

par(mfrow=c(4,5),mgp=c(1.5,0.5,0), oma=c(0,2.5,0,0.5),mar=mar1,tcl=-0.3)

plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
rasterImage(image=panel5b,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")

plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
plot.new()
plot.new()

plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-1,1))

plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% pasture",ylab="")
plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% developed-open space",ylab="")

mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
mtext(expression(paste("long sin(",phi,")",sep="")),2,at=1/8+fudge,outer=T,line=0,cex=0.7)
mtext("long coherence",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
mtext(expression(paste("short cos(",phi,")",sep="")),2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)

>>>>

source("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/bandtest_coh.R")

@@

print(cbind(coh.chlaXaccndvi$lagoslakeid, coh.chlaXaccndvi$accndvip.ts1)[coh.chlaXaccndvi$accndvip.ts1>0.9,])
print(cbind(coh.chlaXaccndvi$lagoslakeid, coh.chlaXaccndvi$accndvip.ts2)[coh.chlaXaccndvi$accndvip.ts2>0.9,])

@@

#plotting
tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_distributions_20191031.tif", units="in",
     res=300, width=6.5, height=5)
layout(matrix(1:4,2,2,byrow=T),heights=c(0.4,0.4,0.6,0.6))

par(mar=c(3,3,2,1),mgp=c(1.7,0.5,0),cex.main=0.9)

@@

par(mar=c(1,1,2,1))
rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phase",
       at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
text(0.9*par()$usr[1],0.95*par()$usr[4],"c)")
rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phase",
     at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
text(0.9*par()$usr[1],0.95*par()$usr[4],"d)")

@@

cohid<-3370
incohid<-4386

bgcol<-rep("grey",length(lakedata))
bgcol[names(lakedata)=="3370"]<-"red"
bgcol[names(lakedata)=="4386"]<-"blue"

laymat<-matrix(c(1,1,2,3),2,2)

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map_plus.tif",units="in",
     res=300, width=6.5, height=2.75)

layout(laymat, width=c(0.6,0.4,0.4))

par(mar=rep(0,4))
plot(lagosstates, main="",bty="o")
points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.55, col="black",bg=bgcol)
legend("bottomright",pch=c(0,21,21,21),col="black",pt.bg=c("grey","grey","red","blue"),
       legend=c("States in LAGOS-NE","Selected lakes","Coherent lake","Non-coherent lake"),inset=c(0.025,0.01),bty="n")
text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.06*diff(par("usr")[3:4]),"a)")

par(mar=c(2.6,1.1,1.1,0.9), mgp=c(1.4,0.4,0), tcl=-0.3, cex.axis=0.8, cex.lab=0.8)
plot(as.numeric(colnames(lakedata[[paste0(cohid)]])),scale(lakedata[[paste0(cohid)]][1,]),type="l", col="blue", ylim=c(-3,3.5),
     ylab="",xlab="Year",yaxt="n")
lines(as.numeric(colnames(lakedata[[paste0(cohid)]])),scale(lakedata[[paste0(cohid)]][2,]), col="green")
mtext("Coherent lake and landscape", cex=0.8)
legend("topright", lty=1, col=c("blue","green"), legend=c("lake","land"), bty="n", cex=0.8, horiz=T)
text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.1*diff(par("usr")[3:4]),"b)")

plot(as.numeric(colnames(lakedata[[paste0(incohid)]])),scale(lakedata[[paste0(incohid)]][1,]),type="l", col="blue", ylim=c(-2,3.3),
     ylab="",xlab="Year", yaxt="n")
lines(as.numeric(colnames(lakedata[[paste0(incohid)]])),scale(lakedata[[paste0(incohid)]][2,]), col="green")
mtext("Non-coherent lake and landscape", cex=0.8)
text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.1*diff(par("usr")[3:4]),"c)")

@@

#huc2 and huc4 watershed codes
huc_codes<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/match_huc_codes.csv", colClasses = 'character')

@@

# bight=5.5
# bigwd=9
# lagosstates_prj<-spTransform(lagosstates, proj4string(huc8_bdys))
# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png", units="in",
# par(mar=c(0,0,1,0))
# plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),
#      ylim=c(1454000,3012981),lwd=0.5)
# par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex.axis=0.7)
# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png", units="in",
# par(mar=c(0,0,1,0))
# plot(huc_bdys_cohlt,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohlt$coeff)],xlim=c(-91837,2260000),
#      ylim=c(1454000,3012981),lwd=0.5)
# par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohlt$coeff), max(huc_bdys_cohlt$coeff), length.out=5),2), cex.axis=0.7)
# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png", units="in",
# par(mar=c(0,0,1,0))
# plot(huc_bdys_sinphilt,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys_sinphilt$coeff)],xlim=c(-91837,2260000),
#      ylim=c(1454000,3012981),lwd=0.5)
# par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_sinphilt$coeff), max(huc_bdys_sinphilt$coeff), length.out=5),2), cex.axis=0.7)
# panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png")
# panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png")
# panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png")
# mar1<-c(3,1.5,0.5,0.2)
# fudge=1/34
# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_landscape.tif",units="in",res=300,width=bigwd, height=bight)
# par(mfrow=c(4,5),mgp=c(1.5,0.5,0), oma=c(0,2.5,0,0.5),mar=mar1,tcl=-0.3)
# mtext(expression(paste("long sin(",phi,")",sep="")),2,at=1/8+fudge,outer=T,line=0,cex=0.7)
# mtext(expression(paste("short cos(",phi,")",sep="")),2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)

## try out portrait orientation by column

bight=8
bigwd=6.5

@@

png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_bycol.png", units="in",
     res=300, width=bigwd/4, height=bight/5)
par(mar=c(0,0,1,0))
plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),
     ylim=c(1454000,3012981),lwd=0.5)
lines(lagosstates_prj,lwd=0.5)
par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex.axis=0.7)
dev.off()

png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_bycol.png", units="in",
     res=300, width=bigwd/4, height=bight/5)
par(mar=c(0,0,1,0))
plot(huc_bdys_cohlt,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohlt$coeff)],xlim=c(-91837,2260000),
     ylim=c(1454000,3012981),lwd=0.5)
lines(lagosstates_prj,lwd=0.5)
par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohlt$coeff), max(huc_bdys_cohlt$coeff), length.out=5),2), cex.axis=0.7)
dev.off()

png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_bycol.png", units="in",
     res=300, width=bigwd/4, height=bight/5)
par(mar=c(0,0,1,0))
plot(huc_bdys_sinphilt,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys_sinphilt$coeff)],xlim=c(-91837,2260000),
     ylim=c(1454000,3012981),lwd=0.5)
lines(lagosstates_prj,lwd=0.5)
par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_sinphilt$coeff), max(huc_bdys_sinphilt$coeff), length.out=5),2), cex.axis=0.7)
dev.off()

panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_bycol.png")
panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_bycol.png")
panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_bycol.png")

mar1<-c(3,1.5,0.3,0.2)
fudge=1/60

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_bycolumn.tif",units="in",res=300,width=bigwd, height=bight)

par(mfcol=c(5,4),mgp=c(1.5,0.5,0), oma=c(0,1.5,1.5,0.5),mar=mar1,tcl=-0.3)

plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"a)")
plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
rasterImage(image=panel5b,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"b)")
plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"c)")
plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")

plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetld. shoreline",ylab="short phase")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"f)")
plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"g)")
plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"h)")
plot.new()
plot.new()

plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"i)")
plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"j)")
plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"k)")
plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")
plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-0.5,1.5))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"m)")

plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"n)")
plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% pasture",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"o)")
plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% devel.-open space",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"p)")

mtext("Partial residuals",2,outer=T,line=0.1,cex=1)
mtext("short coherence",3,at=1/8+fudge,outer=T,line=0,cex=0.8)
mtext(expression(paste("short cos(",phi,")",sep="")),3,at=1/8+1/4+fudge,outer=T,line=-0.2,cex=0.8)
mtext("long coherence",3,at=1/8+2/4+fudge,outer=T,line=0,cex=0.8)
mtext(expression(paste("long sin(",phi,")",sep="")),3,at=1/8+3/4+fudge,outer=T,line=-0.2,cex=0.8)
